### 2012-02-10 GUIErrorDetector/paper/evaluation.tex
Address the second round of comments

Our experimental objective is three-fold: to demonstrate the effectiveness
of our approach in detecting real errors in multithreaded GUI applications, to 
compare the reflection-aware call graph construction algorithm
with existing ones, and to evaluate the usefulness of the proposed 
error filters.

@@

We use a set of open-source projects from Sourceforge, Google code,
and the Eclipse plugin
market as evaluation subjects. To choose subjects for each supported GUI framework,
we first searched for the framework keywords (e.g., ``Java Swing'' or ``Java SWT'')
in the above three source repositories, and then selected subjects based on the following
criteria. First, the subject must be a Java application, not
an open library. Second, the subject must use multithreading in its implementation.
Third, the subject must have undergone at least two years of active development,
and is listed in the first 3 result pages based on popularity. This permits us
to exclude immature subjects that may contain obvious errors.

We chose subjects belonging to various categories from those subjects satisfying
the above criteria. The subjects used in our experiment are shown in Table~\ref{table:subjects},
which include end-user applications, programming tools, and games.

\begin{myindentpar}{-2mm}
\begin{itemize}%\addtolength{\itemsep}{-0.5\baselineskip}
\Item \textbf{SWT desktop applications.}
%VirgoFTP~\cite{virgo} and FileBunker~\cite{filebunker} are two useful SWT desktop applications.
VirgoFTP~\cite{virgo} implements a simple FTP client based on Java and SWT UI library.
FileBunker~\cite{filebunker} is a file backup application which uses one or more GMail
accounts as its backup repository. ArecaBackup~\cite{areca} offers a local
file backup solution for Linux and Windows.

@@

\Item \textbf{Eclipse plugins.}
HudsonEclipse~\cite{hudson} monitors Hudson build status from Eclipse.
EclipseRunner~\cite{eclipserunner} extends Eclipse's capability to run launch configurations.

@@

\Item \textbf{Swing applications.} %S3dropbox~\cite{s3dropbox} and SudokuSolver~\cite{sudokusolver} are two Swing desktop applications.
S3dropbox~\cite{s3dropbox}  allows users
to drag and drop files to their Amazon S3 accounts. SudokuSolver~\cite{sudokusolver}
computes Sudoku solutions efficiently using mutlithreading execution.

@@

We ran our tool on each subject with three call graph construction
algorithms: RTA~\cite{rta}, 0-CFA, and 1-CFA~\cite{kcfa}.  When running
each call graph construction algorithm on three Android applications, we
used two configurations: with and without the reflection-aware algorithm 
(Section~\ref{sec:cg}).  We did not use more expensive algorithms like $k$-CFA ($k >$ 1),
because they can not scale to our subject programs.

We first inspected the source code of each subject to determine whether any
native methods or project-specific GUI interaction patterns were implemented.
Only SGTPuzzler uses native methods to interact with
the underlying operating system. Thus, we manually checked the possible
Java methods that a native method may call, and then added \annotationnum \CodeIn{@CalledByNativeMethods}
annotations for it. Two subjects MyTracks and Fennec employ a customized pattern
to interact with the GUI framework. For example, in MyTracks, all non-UI
threads are initialized via using the library method \CodeIn{android.os.} \CodeIn{handler.handleCallback}.
% the \CodeIn{safeInvokeXX}
%method in the XXX subject first checks whether the current thread is the UI-thread, and
%then determines whether to direct access a GUI object or wrap the code with
%message passing. 
Thus, we add \filternum user-defined filters for these two subjects.
%to indicate
%that they are safe to be invoked from any thread. 
In this experiment, none of the paper
authors was familiar with the subjects; but we found it is quite easy
to add extra annotations and user-defined filters. All these
manual parts took less than a total of 60 minutes.

For each output
warning, we manually determined its validity by either searching the
bug repository to check whether the same error has been reported before,
or submitting a new bug report, or writing a test driver to reproduce
the error.

@@

As shown Table~\ref{table:results},  our tool found
real errors in each subject program. Using the 1-CFA
call graph algorithm, our tool issued 22 warnings, among
which \bugs warnings reveal \bugs distinct errors (\newbugs are previously unknown),
2 warnings are false positives, and the remaining 8 warnings
are redundant. Section~\ref{sec:reflectionaware} compares with other call graph
construction algorithms.

We submitted all \newbugs new errors
to the subject developers. As of February 2012, 1 error in S3dropbox has been confirmed,
4 errors have been reproduced and validated in our own experimental environment, and
2 errors in FileBunker and ArecaBackup had not been verified by developers yet.

@@

%Figures~\ref{fig:swingerror} amd~\ref{fig:pluginerror} show
%two real errors our tool has found. 
Figure~\ref{fig:swingerror}
shows an invalid thread access error our tool found in S3dropbox.
This error happens when the \CodeIn{deleteCurrentBucket}
call on line 63 throws an exception, making it hard to
detect by testing. We reported this error to the S3dropbox developers. Tom Czarniecki,
a key developer of S3dropbox, confirmed this single-GUI-thread
violation. He mentioned that the S3dropbox project uses
certain design patterns to avoid such violations (e.g.,
actions for UI interaction are encapsulated into a \CodeIn{Worker} interface),
but they still overlooked  the error our tool found.
Another reason they overlooked this violation is because some GUI frameworks like Swing
do not provide any run-time checks for invalid thread accesses. Swing
GUI might not exhibit user-visible faults on many erreoneous executions.
However, as clearly stated in the official documentation~\cite{swing}, %Swing is a single-GUI-threaded GUI toolkit and
accessing Swing GUI objects from non-UI threads risks thread interference
or memory-consistency errors.

>>>>

Our experimental objective is three-fold: to demonstrate the effectiveness
of our approach in detecting real errors in multithreaded GUI applications, to 
compare our call graph construction algorithm
with existing ones, and to evaluate the usefulness of the proposed 
error filters.

@@

We used a set of open-source projects from Sourceforge, Google code,
and the Eclipse plugin
market as evaluation subjects. To choose subjects for each supported GUI framework,
we first searched for the framework keywords (e.g., ``Java Swing'' or ``Java SWT'')
in the above three source repositories, and then selected subjects based on the following
criteria. First, the subject must be a Java application, not
an open library. Second, the subject must use multithreading in its implementation.
Third, the subject must have undergone at least two years of active development,
and it is listed in the first 3 result pages based on popularity. This permits us
to exclude immature subjects that may contain obvious errors.

The subjects used in our experiment (Table~\ref{table:subjects})
include end-user applications, programming tools, and games.

\begin{myindentpar}{-2mm}
\begin{itemize}%\addtolength{\itemsep}{-0.5\baselineskip}
\Item \textbf{SWT desktop applications.}
%VirgoFTP~\cite{virgo} and FileBunker~\cite{filebunker} are two useful SWT desktop applications.
VirgoFTP~\cite{virgo} implements a simple FTP client based on Java and the SWT UI library.
FileBunker~\cite{filebunker} is a file backup application that uses one or more GMail
accounts as its backup repository. ArecaBackup~\cite{areca} offers a local
file backup solution for Linux and Windows.

@@

\Item \textbf{Eclipse plugins.}
HudsonEclipse~\cite{hudson} monitors Hudson build status from Eclipse.
EclipseRunner~\cite{eclipserunner} extends Eclipse's capability of running launch configurations.

@@

\Item \textbf{Swing applications.} %S3dropbox~\cite{s3dropbox} and SudokuSolver~\cite{sudokusolver} are two Swing desktop applications.
S3dropbox~\cite{s3dropbox}  allows users
to drag and drop files to their Amazon S3 accounts. SudokuSolver~\cite{sudokusolver}
computes Sudoku solutions efficiently using mutlithreaded execution.

@@

We ran our tool on each subject with three call graph construction
algorithms: RTA~\cite{rta}, 0-CFA, and 1-CFA~\cite{kcfa}.  When running
each call graph construction algorithm on three Android applications, we
used two configurations: with and without our enhancements
(Section~\ref{sec:cgcon}).  We did not use more expensive algorithms like $k$-CFA ($k >$ 1),
because they do not scale to our subject programs.

We first inspected the source code of each subject to determine whether any
native methods or project-specific GUI interaction patterns were implemented.
Only SGTPuzzler uses native methods to interact with
the underlying operating system. For it, we manually checked the possible
Java methods that a native method may call, and then added \annotationnum \CodeIn{@CalledByNativeMethods}
annotations for it. Two subjects MyTracks and Fennec employ a customized pattern
to interact with the GUI framework. For example, in MyTracks, all non-UI
threads are initialized via using the library method \CodeIn{android.os.} \CodeIn{handler.handleCallback}.
% the \CodeIn{safeInvokeXX}
%method in the XXX subject first checks whether the current thread is the UI-thread, and
%then determines whether to direct access a GUI object or wrap the code with
%message passing. 
We added \filternum user-defined filters for these two subjects.
%to indicate
%that they are safe to be invoked from any thread. 
In this experiment, none of the paper
authors was familiar with the subjects; but we found it is quite easy
to add extra annotations and user-defined filters. All these
manual parts took less than a total of 60 minutes.

For all \subnum programs, we manually determined validity of each output warning
by either searching the
bug repository to check whether the same error has been reported before,
or submitting a new bug report, or writing a test driver to reproduce
the error.

@@

As shown Table~\ref{table:results},  our tool found
real errors in each subject program. Using the 1-CFA
call graph algorithm, our tool issued 22 warnings, among
which \bugs warnings reveal \bugs distinct errors (\newbugs were previously unknown),
2 warnings are false positives, and the remaining 8 warnings
are redundant. Section~\ref{sec:reflectionaware} compares with other call graph
construction algorithms.

We submitted all \newbugs new errors
to the subject developers. As of February 2012, 1 error in S3dropbox has been confirmed,
4 errors have been reproduced and validated in our own experimental environment, and
2 errors in FileBunker and ArecaBackup had not yet been verified by developers.

@@

%Figures~\ref{fig:swingerror} amd~\ref{fig:pluginerror} show
%two real errors our tool has found. 
Figure~\ref{fig:swingerror}
shows an invalid thread access error our tool found in S3dropbox.
This error happens when the \CodeIn{deleteCurrentBucket}
call on line 63 throws an exception, making it hard to
detect by testing. We reported this error to the S3dropbox developers. Tom Czarniecki,
a key developer of S3dropbox, confirmed this single-GUI-thread
violation. He mentioned that the S3dropbox project uses
certain design patterns to avoid such violations (e.g.,
actions for UI interaction are encapsulated into a \CodeIn{Worker} interface),
but the developers still overlooked  the error our tool found.
Another reason they overlooked this violation is because some GUI frameworks like Swing
do not provide any run-time checks for invalid thread accesses. The Swing
GUI does not exhibit user-visible faults on some erreoneous executions.
However, as clearly stated in the official documentation~\cite{swing}, %Swing is a single-GUI-threaded GUI toolkit and
accessing Swing GUI objects from non-UI threads risks thread interference
or memory-consistency errors.

### 2012-02-10 GUIErrorDetector/paper/implementation.tex
Address the second round of comments

\item \textbf{UI-accessing nodes: } the \CodeIn{Widget.checkWidget}
and \CodeIn{Display.} \CodeIn{checkDevice} methods. SWT uses the above
two methods to explicitly check whether the current thread is a UI thread,
and throw a \CodeIn{RuntimeException} if the checking fails.
%thread accesses at runtime.
%Any methods for manipulating GUIs object must call (one of) these two methods
% to determine whether the current thread is the UI thread or not.
\smallstep

@@

A Swing application has a single main method, but contains three kinds of
threads: the \textit{initial thread} that executes initial application code from the main method,
the \textit{UI thread}, where all GUI manipulation code is executed,
and the \textit{worker thread} where time-consuming background tasks are executed.
After a Swing program starts, its initial thread exits and the UI thread takes charge
of the application and starts to execute all event-handling code or spawns new worker threads. 
We instantiated our technique for Swing as follows:

@@

\item \textbf{Safe UI methods: } 
\CodeIn{SwingUtilities.}\CodeIn{invokeLater} and \CodeIn{Swing-\\Utilities.invokeAndWait} that execute code on the UI thread.

@@

\item \textbf{Safe UI methods: } \CodeIn{View.post}
and \CodeIn{View.postDelay} that execute code on the UI thread.

@@

We implemented our error detection tool using
the WALA framework~\cite{walatutorial}.
Our tool takes Java bytecode as input, 
automatically detects potential invalid thread access
errors, and scales to realistic programs.  
We implemented the reflection-aware call graph construction
 algorithm (Section~\ref{sec:cg}) using WALA's \textit{bypass logic}.
Unlike existing tools~\cite{Payet:2011:SAA:2032266.2032299}, our tool
does not require a separate pass for program instrumentation; instead, it
parses the configuration file in an Android application,
and then intercepts the call graph construction
process on-the-fly to replace all reflection calls with object creation statements.
Since Android applications are often fully encrypted and shipped in Dalvik
bytecode as a single apk file, our tool first uses
android-apktool~\cite{apktool} to
decrypt the apk file, and then uses the 
ded translator~\cite{ded} to convert
Dalvik bytecode to Java bytecode before feeding to WALA.  The Android system
library (i.e., \CodeIn{android.jar}) uses many ``stub'' classes as
placeholders for the sake of efficiency. We manually re-compiled 
\CodeIn{android.jar} from its source code, so it contains real
class files rather than stubs.

>>>>

\item \textbf{UI-accessing nodes: } the \CodeIn{Widget.checkWidget}
and \CodeIn{Display.} \CodeIn{checkDevice} methods. SWT performs
runtime checking before accessing a GUI object via these methods.
If the current thread is a non-UI thread, the \CodeIn{Widget.checkWidget}
and \CodeIn{Display.checkDevice} methods throw a \CodeIn{RuntimeException}.

@@

A Swing application has a single main method, but contains three kinds of
threads: the \textit{initial thread} that executes initial application code from the main method,
the \textit{UI thread}, where all GUI manipulation code is executed,
and the \textit{worker thread} where time-consuming background tasks are executed.
After a Swing program starts, its initial thread exits and the UI thread takes charge
of the application and starts to execute event-handling code or spawn new worker threads. 
We instantiated our technique for Swing as follows:

@@

\item \textbf{Safe UI methods: } 
\CodeIn{SwingUtilities.}\CodeIn{invokeLater} and \CodeIn{Swing-\\Utilities.invokeAndWait}, which execute code on the UI thread.

@@

\item \textbf{Safe UI methods: } \CodeIn{View.post}
and \CodeIn{View.postDelay}, which execute code on the UI thread.

@@

We implemented our error detection tool using
the WALA framework~\cite{walatutorial}.
Our tool takes Java bytecode as input, 
automatically detects potential invalid thread access
errors, and scales to realistic programs.  
We implemented the reflection-aware call graph construction
 algorithm (Section~\ref{sec:cg}) using WALA's \textit{bypass logic}.
Unlike other tools~\cite{Payet:2011:SAA:2032266.2032299}, our tool
does not require a separate pass for program instrumentation; instead, it
parses the configuration file in an Android application,
and then intercepts the call graph construction
process on-the-fly to replace all reflection calls with object creation statements.
Since Android applications are often fully encrypted and shipped in Dalvik
bytecode as a single apk file, our tool first uses
android-apktool~\cite{apktool} to
decrypt the apk file, and then uses the 
ded translator~\cite{ded} to convert
Dalvik bytecode to Java bytecode before feeding to WALA.  The Android system
library (i.e., \CodeIn{android.jar}) uses many ``stub'' classes as
placeholders for the sake of efficiency. We manually re-compiled 
\CodeIn{android.jar} from its source code, so it contains real
class files rather than stubs.
